Strategic Factors Influencing Target Prioritization in WWII Aerial Bombing

### 2024-04-19 paper/paper.qmd
modify the title

---
title: "Bayesian Insights into Aerial Bombing Strategies: An Ordered Logistic Regression Analysis of WWII Target Prioritization Against Germany"
author: 
  - Yunzhao Li
thanks: "Code and data are available at: https://github.com/yunzhaol/aerial_bomb_priority.git."
date: today
date-format: long
abstract: "During World War II, the strategic decisions about where and how the Allies bombed German industries played an essential role in the Allied campaign. This study employs Bayesian ordered logistic regression to methodically analyze how different factors—such as the industry type, the launching country, the bomb load, and the number of aircraft—influenced the prioritization of targets. Focusing on the strategic choice to target essential oil refineries, the analysis highlights how these attacks were aimed to cripple Germany's war capabilities effectively. The insights from this research not only clarify the strategic rationale behind the Allies' bombing priorities but also enhance our understanding of their impact on the course of the war."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Strategic Factors Influencing Target Prioritization in WWII Aerial Bombing"
subtitle: "An Analysis of 1939-1945 Allied Targeting Against German Industrial Assets"
author: 
  - Yunzhao Li
thanks: "Code and data are available at: https://github.com/yunzhaol/aerial_bomb_priority.git."
date: today
date-format: long
abstract: "During World War II, the strategic decisions about where and how the Allies bombed German industries played an essential role in the Allied campaign. This study employs Bayesian ordered logistic regression to methodically analyze how different factors—such as the industry type, the launching country, the bomb load, and the number of aircraft—influenced the prioritization of targets. Focusing on the strategic choice to target essential oil refineries, the analysis highlights how these attacks were aimed to cripple Germany's war capabilities effectively. The insights from this research not only clarify the strategic rationale behind the Allies' bombing priorities but also enhance our understanding of their impact on the course of the war."
format: pdf
number-sections: true
bibliography: references.bib
---
